---
title: "HMEQ Loan Default: PCA, t-SNE & Cluster Analysis"
output:
  html_document:
    toc: true
    toc_float: true
    theme: flatly
    code_folding: show
knit: (function(input, ...) {
    rmarkdown::render(input, output_file = "index.html", ...)
  })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                       fig.width = 7, fig.height = 5)
```

This notebook runs the full pipeline (baseline models → PCA → t-SNE →
modeling comparison → clustering) and knits the results straight into a
single HTML report. It's the reproducible counterpart to the static
`report.html` already in this repo — knit this file yourself any time
you update the data or the scripts and want a fresh report.

```{r load-data}
data_path <- "data/HMEQ_Processed.csv"
df <- read.csv(data_path, header = TRUE)
str(df)
```

# Part 1: PCA & t-SNE for Predictive Modeling

## Step 1: Baseline models on the original data

```{r step1, results="hide"}
source("scripts/01_baseline_models.R")
```

## Step 2: PCA analysis

```{r step2}
source("scripts/02_pca_analysis.R")
```

## Step 3: t-SNE analysis

```{r step3, results="hide"}
source("scripts/03_tsne_analysis.R")
```

## Step 4: Models on the original data + PCA/t-SNE columns

```{r step4, results="hide"}
source("scripts/04_models_original_data.R")
```

```{r step4-auc}
auc(roc_obj)
```

## Step 5: Models on PCA/t-SNE features only

```{r step5, results="hide"}
source("scripts/05_models_pca_tsne_data.R")
```

```{r step5-auc}
auc(roc_obj2)
```

Comparing the two AUC values above is the key result of Part 1: the
full feature set clearly outperforms the PCA/t-SNE-only feature set.

# Part 2: PCA + K-Means Cluster Analysis

```{r step6, results="hide"}
source("scripts/06_cluster_analysis.R")
```

```{r cluster-sizes}
final_km$size
```

See `README.md` for the full narrative write-up and figure-by-figure
discussion of these results.
